---
title: "Modeling"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(plm)
library(lmtest)
library(clubSandwich)
library(modelsummary)

options(scipen = 999)

data <- read_csv(here::here("data",
                            "monthly-county-combined-dataset.csv"))



data <- data %>% 
  filter(month >= "2020-01-01",
         month < "2021-03-01") %>% 
  mutate(across(c(cases, deaths),
                ~ ifelse(is.na(.),
                         0,
                         .))) %>% 
  mutate(cases_per_capita = cases / population,
         deaths_per_capita = deaths / population) %>% 
  filter(!is.na(fips))


```


## Models

### Pooled

```{r}

mod_pool_rent <- lm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data)

mod_pool_own <-lm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                  + avg_temp + unemployment_rate,
                  data = data)

modelsummary(list("Rent index" = mod_pool_rent, 
                  "Home price indec" = mod_pool_own),
             stars = TRUE,
             vcov = ~fips)

```


### County fixed effects

```{r}

mod_ind_rent <- plm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "within")

mod_ind_own <- plm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "within")


modelsummary(list("Rent index" = mod_ind_rent, 
                  "Home price index" = mod_ind_own),
             stars = TRUE)

```

### Time fixed effects

```{r}

mod_time_rent <- plm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate + factor(month),
                    data = data,
                    index = c("fips", "month"),
                    model = "within",
                  effect = "time")

mod_time_own <- plm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate + factor(month),
                    data = data,
                   index = c("fips", "month"),
                    model = "within",
                  effect = "time")


modelsummary(list("Rent index" = mod_time_rent, 
                  "Home price index" = mod_time_own),
             stars = TRUE,
             coef_omit = "month")

```

### County and time fixed effects


```{r}

mod_it_rent <- plm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "within",
                   effect = "twoways")

mod_it_own <- plm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                  + avg_temp + unemployment_rate,
                  data = data,
                  index = c("fips", "month"),
                  model = "within",
                  effect = "twoways")

modelsummary(list("Rent index" = mod_it_rent, 
                  "Home price index" = mod_it_own),
             stars = TRUE)


```

### Random effects

```{r}

mod_rand_rent <- plm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "random",
                   effect = "twoways")

mod_rand_own <- plm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                  + avg_temp + unemployment_rate,
                  data = data,
                  index = c("fips", "month"),
                  model = "random",
                  effect = "twoways")


modelsummary(list("Rent index" = mod_it_rent, 
                  "Home price index" = mod_it_own),
             stars = TRUE)


```


### Comparing all models for rents

```{r, warning=FALSE}

modelsummary(list("Pooled" = mod_pool_rent,
                  "County effects" = mod_ind_rent,
                  "Time effects" = mod_time_rent,
                  "County and time fixed effects" = mod_it_rent,
                  "Random effects" = mod_rand_rent),
             vcov = c(~cyl, rep("classical", 4)),
             stars = TRUE,
             coef_omit = "month",
             gof_omit = "AIC|BIC|Log.Lik")


modelplot(list("Pooled" = mod_pool_rent,
                  "County effects" = mod_ind_rent,
                  "Time effects" = mod_time_rent,
                  "County and time fixed effects" = mod_it_rent,
                  "Random effects" = mod_rand_rent),
             vcov = c(~cyl, rep("classical", 4)),
          coef_omit = "month|(Intercept)|deaths_per_capita")
```

### Comparing all models for home prices

```{r, warning=FALSE}

modelsummary(list("Pooled" = mod_pool_own,
                  "County effects" = mod_ind_own,
                  "Time effects" = mod_time_own,
                  "County and time fixed effects" = mod_it_own,
                  "Random effects" = mod_rand_own),
             vcov = c(~cyl, rep("classical", 4)),
             stars = TRUE,
             coef_omit = "month",
             gof_omit = "AIC|BIC|Log.Lik")


modelplot(list("Pooled" = mod_pool_own,
                  "County effects" = mod_ind_own,
                  "Time effects" = mod_time_own,
                  "County and time fixed effects" = mod_it_own,
                  "Random effects" = mod_rand_own),
             vcov = c(~cyl, rep("classical", 4)),
          coef_omit = "month|(Intercept)|deaths_per_capita")

```



## Testing specification

### Time effect vs pooled {.tabset .tabset.fade}

#### Rent

```{r}

pFtest(mod_time_rent, mod_pool_rent)

```

#### Home price

```{r}

pFtest(mod_time_own, mod_pool_own)

```

### Individial effects vs pooled {.tabset .tabset.fade}

#### Rent

```{r}

pFtest(mod_ind_rent, mod_pool_rent)

```

#### Home price

```{r}

pFtest(mod_ind_own, mod_pool_own)

```

### T+I effects vs. pooled {.tabset .tabset.fade}

#### Rent

```{r} 

pFtest(mod_it_rent, mod_pool_rent)

```

#### Home price

```{r}

pFtest(mod_it_own, mod_pool_own)

```

### T+I effects vs. individual {.tabset .tabset.fade}

#### Rent

```{r}

pFtest(mod_it_rent, mod_ind_rent)

```

#### Own

```{r}

pFtest(mod_it_own, mod_ind_own)

```

### T+I effects vs. time {.tabset .tabset.fade}

#### Rent

```{r}

pFtest(mod_it_rent, mod_time_rent)

```

#### Own

```{r}

pFtest(mod_it_own, mod_time_own)

```



### Random vs pooled {.tabset .tabset.fade}

#### Rent

```{r}

mod_pool_rent2 <- plm(rent_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "pooling")

plmtest(mod_pool_rent2, type = "bp")

```

#### Home price

```{r}

mod_pool_own2 <- plm(zhvi_index ~ cases_per_capita + deaths_per_capita 
                    + avg_temp + unemployment_rate,
                    data = data,
                    index = c("fips", "month"),
                    model = "pooling")

plmtest(mod_pool_own2, type = "bp")

```


### Random vs individual {.tabset .tabset.fade}

#### Rent

```{r}

phtest(mod_ind_rent, mod_rand_rent)

```

#### Home price

```{r}

phtest(mod_ind_own, mod_rand_own)

```

### Random vs. T+I {.tabset .tabset.fade}

#### Rent

```{r}

phtest(mod_it_rent, mod_rand_rent)

```

#### Home price

```{r}

phtest(mod_it_own, mod_rand_own)

```
